plots with prolactin

### 2019-12-07 analysis/16_PRL.Rmd
new prl images

```{r data}
hormones <- read_csv("../results/hormones.csv")
hormones$treatment <- factor(hormones$treatment, levels = alllevels)
```

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
    geom_boxplot() +
  ylim(c(-10,120)) + 
    mytheme() +
  #theme(axis.text.x = element_blank()) + 
  theme(legend.position = "none") + 
  labs(x = "parental care stages", y = "prolactin conc. (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5) 
p1

meanPRL <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = mean(plasma_conc), 
                   se = sd(plasma_conc)/sqrt(length(plasma_conc))) %>%
  dplyr::mutate(m = round(m,0)) 
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = alllevels)
meanPRL

ggplot(meanPRL, aes(treatment, m)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se), width=.1) +
   geom_image(aes(image=iconpath), size=.12)  +
  labs(x = "parental care stages", y = "Prolactin (ng/mL)")

ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Prolactin (ng/mL)")  +
  mytheme() +
  ylim(c(-15,80)) +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5)

p2 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = as.numeric(treatment), y = plasma_conc)) +
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    mytheme() +
    theme(axis.text.x = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin conc. (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "parental care stages", y = "prolactin conc. (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120)) 
p2
```

@@

p3 <- ggplot(candidates.pit, aes(x = as.numeric(treatment), y = PRL)) + 
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment, alpha = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    mytheme() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "PRL expression in the pituitary", x = "parental care stage") +
    scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
                       labels = charlevels) +
  annotation_custom(control, ymin = 12, ymax = 14, xmin = -7.8) +
  annotation_custom(bldg, ymin = 12, ymax = 14, xmin = -5.8) +
  annotation_custom(lay, ymin = 12, ymax = 14, xmin = -3.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = -1.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 0.6) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 2.4) +
  annotation_custom(hatch, ymin = 12, ymax = 14, xmin = 4.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 6.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 8.4)  + 
  ylim(c(13,24)) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) 
p3

candidates.pit

meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = mean(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,0)) 
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = alllevels)
meanPRL

ggplot(meanPRL, aes(treatment, m)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se), width=.1) +
   geom_image(aes(image=iconpath), size=.12)  +
  labs(x = "parental care stages", y = "Pituitary PRL expression")

ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Pituitary PRL expression") +
  mytheme() +
  ylim(c(15,22)) +
  annotation_custom(control, ymin = 15, ymax = 16.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 15, ymax = 16.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 15, ymax = 16.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 15, ymax = 16.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 8.5) 
```

>>>>

```{r data}
hormones <- read_csv("../results/hormones.csv")
hormones$treatment <- factor(hormones$treatment, levels = alllevels)

meanprolactin <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = mean(plasma_conc), 
                   se = sd(plasma_conc)/sqrt(length(plasma_conc))) %>%
  dplyr::mutate(m = round(m,0)) 
meanprolactin <- left_join(meanprolactin, birds)
meanprolactin$treatment <- factor(meanprolactin$treatment, levels = alllevels)
meanprolactin

```

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
    geom_boxplot() +
  ylim(c(-10,120)) + 
    theme_B3() +
  #theme(axis.text.x = element_blank()) + 
  theme(legend.position = "none") + 
  labs(x = "parental care stages", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5) 
p1

p2 <-  ggplot(meanprolactin, aes(treatment, m)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image=iconpath), size=.1)  +
  labs(x = "parental care stages", y = "prolactin (ng/mL)") +
  theme_B3() +
  theme(legend.position = "none")

p2

p3 <- ggplot(meanprolactin, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "increasing time >>", y = "prolactin (ng/mL)")  +
  mytheme() +
  ylim(c(-15,80)) +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5) +
  geom_hline(yintercept=0) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=40) +
  geom_hline(yintercept=60) +
  geom_hline(yintercept=80) 
p3

p4 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc)) +
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120)) 
p4

plot_grid(p1,p4,p2,p3)

```

@@

meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = mean(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,1)) 
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = alllevels)
meanPRL

p5 <- candidates.pit %>% 
  ggplot(aes(x = treatment, y = PRL, fill = treatment)) +
    geom_boxplot() +
    theme_B3() +
  theme(legend.position = "none") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = 12, ymax = 14, xmin = -7.8) +
  annotation_custom(bldg, ymin = 12, ymax = 14, xmin = -5.8) +
  annotation_custom(lay, ymin = 12, ymax = 14, xmin = -3.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = -1.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 0.6) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 2.4) +
  annotation_custom(hatch, ymin = 12, ymax = 14, xmin = 4.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 6.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 8.4)  +
  ylim(c(13,24)) 
p5

p6 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "PRL expression in the pituitary", x = "parental care stage") +
  annotation_custom(control, ymin = 12, ymax = 14, xmin = -7.8) +
  annotation_custom(bldg, ymin = 12, ymax = 14, xmin = -5.8) +
  annotation_custom(lay, ymin = 12, ymax = 14, xmin = -3.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = -1.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 0.6) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 2.4) +
  annotation_custom(hatch, ymin = 12, ymax = 14, xmin = 4.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 6.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 8.4)  + 
  ylim(c(13,24)) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) 
p6

p7 <- ggplot(meanPRL, aes(treatment, m)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image=iconpath), size=.12)  +
  labs(x = "increasing time >>", y = "Pituitary PRL expression") +
  theme_B3()  +
  theme(legend.position = "none")
p7

p8 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Pituitary PRL expression") +
  mytheme() +
  ylim(c(15,22)) +
  annotation_custom(control, ymin = 15, ymax = 16.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 15, ymax = 16.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 15, ymax = 16.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 15, ymax = 16.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 8.5)   +
  geom_hline(yintercept=17) +
  geom_hline(yintercept=18) +
  geom_hline(yintercept=19) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=21)

p8

plot_grid(p5,p6,p7,p8)
```

## prolactin manip

```{r manipdata}
vsd.pit <- readvsd("../results/06_pitallvsd.csv")
vsd.pit$entrezid <- row.names(vsd.pit)

colData.pit <- read_csv("../metadata/00_samples.csv") %>% 
  filter(tissue == "pituitary") %>% 
  mutate(sample = V1)

geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  
  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)

candidategenes <- c("PRL")
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)
candidates.pit$treatment <- factor(candidates.pit$treatment, levels = alllevels)

meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = median(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,1)) 
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = alllevels)
meanPRL
```

```{r PRL.pit.maip}
p10 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image = iconpath), size = 0.06)  +
   geom_image(aes(image = music , y = m + 0.5), size = 0.04) +
   labs(x = "parental care stages", y = "Pituitary PRL") +
   mytheme() +
   ylim(c(16,22)) +
   theme(axis.text.x = element_text(angle = 45)) +
  theme(legend.position = "none") +
  scale_color_manual(values = colorscharmaip2) +
  geom_hline(yintercept=16.8) +
  geom_hline(yintercept=17.8) +
  geom_hline(yintercept=18.8) +
  geom_hline(yintercept=19.8) +
  geom_hline(yintercept=20.8)  
p10

p11 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
       geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(c(13,22.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -14.8) +
  annotation_custom(bldg, ymin = 13, ymax = 14, xmin = -12.8) +
  annotation_custom(lay, ymin = 13, ymax = 14, xmin = -10.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -8.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -6.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -4.8) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = -2.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -0.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = 1.4) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = 3.4)  +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 5.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 7.4) +
  annotation_custom(removechick, ymin = 13, ymax = 14, xmin = 9.4) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 11.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 13.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 15.4) 
p11

p12 <- candidates.pit %>%
  filter(treatment %in% c("inc.d9", "m.inc.d8", "hatch")) %>%
    ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  ylim(c(13,22.5)) +
  scale_fill_manual(values = colorscharmaip2)   +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -1.6) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 0.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 2.4)
p12

p13 <- candidates.pit %>%
  filter(treatment %in% c("inc.d17", "prolong", "hatch")) %>%
    ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  ylim(c(13,22.5)) +
  scale_fill_manual(values = colorscharmaip2)   +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -1.6) +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 0.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 2.4)
p13

p14 <- candidates.pit %>%
  filter(treatment %in% c("hatch", "extend", "n5")) %>%
    ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  ylim(c(13,22.5)) +
  scale_fill_manual(values = colorscharmaip2)   +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -1.6) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 0.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 2.4)
p14

plot_grid(p12,p13 + theme(axis.text.y = element_blank(), axis.title.y = element_blank()),
          p14 + theme(axis.text.y = element_blank(), axis.title.y = element_blank()), 
          nrow = 1, rel_widths = c(1.2,1,1))

```

```{r geneshormones}
candidates.pit$bird_id <- candidates.pit$bird

geneshormones <- left_join(candidates.pit, hormones) %>%
  select(-X1, -V1, -okay, - icons, -music, -iconpath) %>%
  drop_na()
head(geneshormones)

ggplot(geneshormones, aes(x = plasma_conc, y = PRL)) +
  geom_point(aes(color = treatment)) +
  facet_wrap(~hormone, scales = "free_x") +
    geom_smooth(method = "lm", color = "grey")

prolactin2 <- read_csv("../results/07_prolactin2.csv")
head(prolactin2)
geneshormones2 <- left_join(candidates.pit, prolactin2) %>%
  drop_na()
head(geneshormones)

ggplot(geneshormones2, aes(x = plasma_conc, y = PRL)) +
  geom_point(aes( color = treatment)) +
  geom_smooth(method = "lm", color = "grey") +
  facet_wrap(~hormone, scales = "free") 
```

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
```
